A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-23 paper/paper.tex
paper: update diagrams; include UIP_refl

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
\usepackage[prefix=bonak]{art.cls/xkeymask}

@@

\iffalse
  Our contribution is the following. We have modelled the core of semi-simplicial sets in a way that naturally generalizes to semi-cubical sets in type theory, and we call our generalization \emph{$\nu$-sets}. In contrast to the presheaf presentation of semi-cubical -based where the set of  that use a fibered representation, we use an indexed representation. Our work is, in principle axiom-free, although the accompanying artifact uses functional extensionality, and this requires disappears if $\nu$ is finite.
\fi

@@

\begin{example}[$\DeltaPlus^0$, $\DeltaPlus^1$]
  $\DeltaPlus^0$ can be drawn as:

  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, dash] & 1
    \end{tikzcd}
  \end{equation*}

  $\DeltaPlus^1$ can be drawn as a filled triangle:

  \begin{equation*}
    \begin{tikzcd}
      & 2 \arrow[dr, dash] & \\
      0 \arrow[rr, dash]\arrow[ur, dash] && 1
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\begin{example}[$\Cube^0$, $\Cube^1$ and $\Cube^2$]
  $\Cube^0$ can be drawn as:

  \begin{equation*}
    \begin{tikzcd}
      0 \equiv 1
    \end{tikzcd}
  \end{equation*}

  $\Cube^1$ can be drawn as:

  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, dash] & 1
    \end{tikzcd}
  \end{equation*}

  and $\Cube^2$ can be drawn as a filled square:

  \begin{equation*}
    \begin{tikzcd}
      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{theorem}
  $\CSet$ does not admit degeneracies.
  \begin{proof}
    The reader is advised to refer to \cite{Antolini00} for the proof.
  \end{proof}
\end{theorem}

@@

In type theory, UIP can be proved on the unit type:

\begin{align*}
  \mathsf{eq\_refl}        & : \forall x, x = x                                                    \\
  \mathsf{UIP\_refl\_unit} & : \forall x : \unitpoint = \unitpoint, x = \mathsf{eq\_refl}          \\
  \mathsf{UIP\_refl\_bool} & : \forall b : \mathsf{bool}, \forall x : b = b, x = \mathsf{eq\_refl} \\
\end{align*}

@@

  \bibitem[CubSet]{Antolini00}
  Antolini, R. (2000). Cubical structures, homotopy theory. \emph{Annali di Matematica pura ed applicata, 178}(1), 317-324.

>>>>

\usepackage{multirow, float, tabularx, environ, booktabs, setspace, makecell, caption, art.cls/joinargs, colortbl, pdflscape}
\usepackage[prefix=bonak]{art.cls/xkeymask}
\usepackage[skip=0.4em]{parskip}

@@

@@

\begin{definition}[$\DeltaPlus^n$]
  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as:
\end{definition}

We now illustrate the standard augmented $n$-semi-simplices for dimensions $1$, $2$, and $3$.

\begin{example}[$\DeltaPlus^1$]
  In dimension $1$, the standard augmented semi-simplex is simply the unit type:

  \begin{equation*}
    \begin{tikzcd}
      0
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\DeltaPlus^2$]
  \begin{equation*}
    \begin{tikzcd}
      \star0 \arrow[r, dash, "\star\star"] & 0\star
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\DeltaPlus^3$]
  \begin{equation*}
    \begin{tikzcd}
      & 00\star \arrow[dr, dash, "0\star\star"] & \\
      \star00 \arrow[rr, dash, "\star\star0"]\arrow[ur, dash, "\star0\star"] && 0\star0
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\begin{definition}[$\Cube^n$]
  The standard semi-cube $\Cube^n$ is defined as:
\end{definition}

We now illustrate the standard $n$-semi-cubes for dimensions $0$, $1$, and $2$.

\begin{example}[$\Cube^0$]
  $\Cube^0$ can be drawn as:

  \begin{equation*}
    \begin{tikzcd}
      \{\}
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\Cube^1$]
  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, "\star", dash] & 1
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\Cube^2$]
  \begin{equation*}
    \begin{tikzcd}
      (0, 1) \arrow[r, dash] & (1, 1) \arrow[d, dash] \\
      (0, 0) \arrow[u, dash] & (1, 0) \arrow[l, dash]
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{remark}
  $\CSet$ does not admit degeneracies.
\end{remark}

@@

An equivalent defintion of UIP is given by \textsf{UIP\_refl}:

\begin{align*}
  \textsf{UIP\_refl} & : \forall x, \forall p : x = x, p = \textsf{eq\_refl } x
\end{align*}

In type theory, UIP can be proved on the unit type and bool type:

\begin{align*}
  \textsf{eq\_refl}        & : \forall x, x = x                                                    \\
  \textsf{UIP\_refl\_unit} & : \forall u : \textsf{unit}, \forall x : u = u, x = \textsf{eq\_refl} \\
  \textsf{UIP\_refl\_bool} & : \forall b : \textsf{bool}, \forall x : b = b, x = \textsf{eq\_refl} \\
\end{align*}

@@
